%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects and Open Source Contributions}

\begin{cvparagraph}
	A small sample of projects and open source contributions that I have made in the last couple of years.
\end{cvparagraph}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {\href{https://github.com/druid-io/druid/commits?author=erikdubbelboer}{\textcolor{link}{https://github.com/druid-io/druid/commits?author=erikdubbelboer}}} % Institution
    {Druid} % Degree
    {Java} % Location
    {2016 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
				\item{I contributed many improvements to Druid, a high-performance, column-oriented, distributed data store.}
      \end{cvitems}
    }

  \cventry
    {\href{https://github.com/erikdubbelboer/phpRedisAdmin}{\textcolor{link}{https://github.com/erikdubbelboer/phpRedisAdmin}}} % Institution
    {phpRedisAdmin} % Degree
    {PHP} % Location
    {2011 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
				\item{A Simple web interface to manage Redis databases.}
      \end{cvitems}
    }

  \cventry
    {\href{https://github.com/erikdubbelboer/discnt}{\textcolor{link}{https://github.com/erikdubbelboer/discnt}}} % Institution
    {Discnt} % Degree
    {C} % Location
    {2015 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
				\item{Distributed eventually consistent counters.}
				\item{We use this at atomx.com to sync campaign budgets in realtime between multiple datacenters around the world.}
      \end{cvitems}
    }

  \cventry
    {\href{https://github.com/erikdubbelboer/fasthttp}{\textcolor{link}{https://github.com/erikdubbelboer/fasthttp}}} % Institution
    {fasthttp} % Degree
    {Go} % Location
    {2017 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
				\item{I maintain the only actively maintained fork of the popular fasthttp Go package.}
      \end{cvitems}
    }

  \cventry
    {\href{https://github.com/samizdatco/nginx-http-auth-digest/graphs/contributors}{\textcolor{link}{https://github.com/samizdatco/nginx-http-auth-digest/graphs/contributors}}} % Institution
    {nginx-http-auth-digest} % Degree
    {C} % Location
    {2016 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
				\item{I maintain the nginx-http-auth-digest module which provides Digest authentication to Nginx.}
      \end{cvitems}
    }

  \cventry
		{\href{https://github.com/erikdubbelboer/redis-lua-scaling-bloom-filter}{\textcolor{link}{https://github.com/erikdubbelboer/redis-lua-scaling-bloom-filter}}}
    {redis-lua-scaling-bloom-filter} % Degree
    {Lua} % Location
    {2012 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
				\item{LUA Redis scripts for a scaling bloom filters.}
      \end{cvitems}
    }

  \cventry
		{\href{https://github.com/erikdubbelboer/OS-Tutorial}{\textcolor{link}{https://github.com/erikdubbelboer/OS-Tutorial}}}
    {OS Tutorial} % Degree
    {C/ASM} % Location
    {2010} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
				\item{I wrote an example on how to use GRUB to boot a small operating system running in paged virtual memory.}
      \end{cvitems}
    }

  \cventry
		{\href{https://blog.dubbelboer.com/2012/11/18/brainfuck-jit.html}{\textcolor{link}{https://blog.dubbelboer.com/2012/11/18/brainfuck-jit.html}}}
    {Brainfuck JIT} % Degree
    {C} % Location
    {2012} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
			\item{I wrote a JIT Brainfuck interpreter using GNU lightning.}
      \end{cvitems}
    }

  \cventry
		{\href{https://github.com/erikdubbelboer/libuv-lua-http-server}{\textcolor{link}{https://github.com/erikdubbelboer/libuv-lua-http-server}}}
    {libuv-lua-http-server} % Degree
    {C} % Location
    {2013} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
				\item{Simple example webserver using Libuv and LUA.}
      \end{cvitems}
    }

  \cventry
    {\href{https://github.com/golang/go/commits?author=erikdubbelboer}{\textcolor{link}{https://github.com/golang/go/commits?author=erikdubbelboer}}} % Institution
    {Golang} % Degree
    {Go} % Location
    {2015 - 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
				\item{Minor speed improvement and fixes for the Go programming language.}
      \end{cvitems}
    }

  \cventry
    {\href{https://github.com/pquerna/ffjson/commits?author=erikdubbelboer}{\textcolor{link}{https://github.com/pquerna/ffjson/commits?author=erikdubbelboer}}} % Institution
    {ffjson} % Degree
    {Go} % Location
    {2016 - 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
				\item{Bug fix and additional features for ffjson, the fast JSON serialization for Go.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
