%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {CTO and Founder} % Job title
    {Atomx.com} % Organization
    {Kuala Lumpur, Malaysia} % Location
    {Jan. 2015 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
				\item {I designed and build most of the platform on Google Cloud.}
				\item {At it's peak Atomx was handling 4.5 billion requests per day (around 50.000 per second).}
				\item {All high throughput low latency systems written in Go.}
				\item {Using Kafka and Druid for realtime reporting.}
				\item {Other technologies used: Nginx, Aerospike, Redis, Rethinkdb and MySQL.}
				\item {Check \href{https://www.atomx.com/}{\textcolor{link}{https://www.atomx.com/}} for more information.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {CTO and Founder} % Job title
    {Adperium B.V.} % Organization
    {Utrecht, Netherlands} % Location
    {Jun. 2009 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
				\item {Adperium is an advertising network that works with big publishers (Alexa top-500 website) and premium advertisers.}
				\item {Check \href{https://www.adperium.com/}{\textcolor{link}{https://www.adperium.com/}} for more information.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {President and Founder} % Job title
    {Mininova.org} % Organization
    {Utrecht, Netherlands} % Location
    {Jan. 2005 - Apr. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
				\item {I wrote a lot of the code and did a lot of optimizations.}
				\item {The website was written in PHP using MySQL as storage.}
				\item {At its peak Mininova was handling 30 million pageviews from 7 million unique visitors per day.}
				\item {The word ‘mininova’ ranked 9 on \href{https://archive.google.com/press/zeitgeist2006.html}{\textcolor{link}{Google’s list of most queried terms in 2006}}.}
				\item {On fabruary 18 2008 Alexa.com ranked mininova as 54th biggest website on the internet.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
